\subsubsection{Augmented Datasets}
\label{experiments:03.4.1:backbone_prost:Augmented}
As with the Med-NCA in the second trial, we trained a total of 3k epochs each for the comparison. The comparison model was trained directly on the DiceBCE for 3k epochs. The test model was pretrained for 2k epochs on the DiceBCE and then trained for another 1k epochs on the DiceBceNQM. The results can be seen in \autoref{tab:03.4.1:Backbone_Prost:on_Spike}. We have trained a total of one cohort on the prostate spikes.

The results are similar to the augmentations with the Med-NCA (3k epochs) \autoref{tab:03.2.1:medNCA_Prost:on_Spike:3kepochs}. However, the models diverge even more. Overall, however, the trend does not look worse. Only the model trained on the fully augmented dataset Spike 1.0 performs significantly worse on the DiceBceNQM, with -6 points on the Dice. On the original dataset, as well as on Spike 0.3 and Spike 0.1, it tended to perform better, with +3 and +4 points, respectively. On the other two datasets, especially the attractive, less augmented dataset Spike 0.01, the model performed 1-2 points worse. This was similar for the Med-NCA, although the scores were distributed slightly differently, suggesting that the dataset rather than the model is more challenging in terms of transferability than the hippocampus dataset, but this would need to be verified with more datasets.

%%% aggregated table ... no use here %%%
\iffalse
\begin{table}[h!]
    \centering
    \begin{tabular}{|l|l|l|l|l|}
        \hline
        \bfseries & mean on signed & mean on absolute & sum on absolute & range\\\hline
        % ---
        \bfseries & 0.0008 & 0.0136 & 0.49 & (-0.055, 0.04)\\\hline
        % ---
    \end{tabular}
    \caption{Agreggations over the improvements$(+)$ and deteriorations$(-)$, using the DiceBceNQM compared to the DiceBCE on Dice. For the Backbone-NCA on the Spike Postate Datasets. All values of the experiments used for this Aggregations: \autoref{tab:03.4.1:Backbone_Prost:on_Spike}}
    \label{tab:3.4.1:Backbone_Prost:on_Spike_aggregated}
\end{table}
\fi
%%% tables %%%
\iftable
\input{content/experiments/03_Robustness_Improving/03.4_Backbone_and_Prostate/tables/table_03.4.1_Augmented_Spikes}
\input{content/experiments/03_Robustness_Improving/03.2_medNCA_and_Prostate/tables/table_03.2.1_Spike_3k}
\fi